---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# miceafter

The package provides functions to apply statistical analyses after multiple imputation. Therefore the name 'miceafter'. The main functions of the package are the `df2milist`, `list2milist`, `mids2milist` and the `with.milist` functions. The `df2milist` function turns a data frame with multiply imputed datasets into an object of class `milist`, the `list2milist` does this for a list with multiply imputed datasets and the `mids2milist` for objects of class `mids`. These `milist` object can than be used with the `with.milist` function to apply repeated statistical analyses across the multiply imputed datasets. Subsequently, pooling functions are available in the form of separate `pool` functions, like the `pool_levenetest` function to pool Levene's tests across multiply imputed datasets. The package also contains a function `glm_mi` to pool and select linear and logistic regression functions.   

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mwheymans/miceafter")
```

## Citation

Cite the package as:

``` r

Martijn W Heymans (2021). miceafter: Data Analysis and Pooling after Multiple Imputation. 
R package version 0.1.0. https://mwheymans.github.io/miceafter/

```
## Examples

## Pooling Levene's Test

This example shows you how to pool the Levene test across 5 multiply imputed datasets. The pooling method that is used is method D1.

```{r }

library(miceafter)

# Step 1: Turn data frame with multiply imputed datasets into object of 'milist'
imp_dat <- df2milist(lbpmilr, impvar="Impnr")

# Step 2: Do repeated analyses across multiply imputed datasets
ra <- with(imp_dat, expr=levene_test(Pain ~ factor(Carrying)))

# Step 3: Pool repeated test results
res <- pool_levenetest(ra, method="D1")
res

```

## Pooling Difference between Proportions according to Newcombe-Wilson

```{r }

library(miceafter)

# Step 1: Turn data frame with multiply imputed datasets into object of 'milist'
imp_dat <- df2milist(lbpmilr, impvar="Impnr")

# Step 2: Do repeated analyses across multiply imputed datasets
ra <- with(imp_dat, 
           expr=propdiff_wald(Chronic ~ Radiation, strata = TRUE))

# Step 3: Pool repeated test results
res <- pool_propdiff_nw(ra)
res

```

More examples can be found on the [package website](https://mwheymans.github.io/miceafter/)
